### 2024-08-15 machine-learning.qmd
20240815 - evaluate accuracy

@@

```{r}
gp_model_fit_qb <- gpb.train(
  data = gp_data_qb,
  gp_model = gp_model_qb,
  nrounds = nrounds,
  params = params_qb) # verbose = 0

@@

y_pred_test_qb <- pred_test_qb[["response_mean"]]
cbind(y_pred_test_qb, data_test_qb_matrix[,"fantasyPoints_lag"])
mean((data_test_qb_matrix[,"fantasyPoints_lag"] - y_pred_test_qb)^2)
```

>>>>

nrounds_qb <- 7000 # identify optimal number of trees through iteration and cross-validation

@@

```{r}
gp_model_fit_qb <- gpb.train(
  data = gp_data_qb,
  gp_model = gp_model_qb,
  nrounds = nrounds_qb,
  params = params_qb) # verbose = 0

@@

y_pred_test_qb <- pred_test_qb[["response_mean"]]
cbind(y_pred_test_qb, data_test_qb_matrix[,"fantasyPoints_lag"])

petersenlab::accuracyOverall(
  predicted = y_pred_test_qb,
  actual = data_test_qb_matrix[,"fantasyPoints_lag"],
  dropUndefined = TRUE
)
```
